APIs for hyperparameter optimization in scikit-learn

### 2013-05-13 paper.tex
two-column layout for more realistic view of final paper
copyedit

\documentclass[a4paper]{article}

@@

The main goal of the scikit-learn project
is to provide high-quality implementations
of ``classic'' machine learning algorithms
with a consistent API.
This paper explores the role that such an API plays
for handling the problem of hyperparameter optimization,
or \textit{model selection} as it is called in the statistics literature.

@@

While direct use of this idiom would not have any benefit
over using the individual stages of the sub-pipeline directly,
the recursion support shines when in more complex situations
that involve the construction of estimators using \textit{meta-estimators}.
These are objects in the scikit-learn API
that wrap an estimator to give it additional functionality.
An example of meta-estimators are object of the class
\texttt{OneVsRestClassifier},
which can be used to construct a multi-label classifier
\citep{tsoumakas2007multi}
from an ordinary binary classifier object
by constructing one binary classifier per class
(a strategy variously called one-vs.-the-rest,
one-vs.-all or binary relevance).

>>>>

\documentclass[a4paper,twocolumn]{article}

@@

The main goal of the scikit-learn project
is to provide high-quality implementations
of ``classic'' machine learning algorithms
with a consistent API.
This paper explores the role that such an API plays
for handling the problem of hyperparameter optimization,
also known as \textit{model selection} (\citealp{elemstatlearn}:219--257).

@@

Direct use of this idiom would not have any benefit
over using the individual stages of the sub-pipeline directly,
as both approaches would simply produce a linear pipeline.
However, the recursion support shines in more complex situations
that involve the construction of estimators using \textit{meta-estimators}.
These are objects in the scikit-learn API
that wrap an estimator to give it additional functionality.
An example of meta-estimators are object of the class
\texttt{OneVsRestClassifier},
which can be used to construct a multi-label classifier
\citep{tsoumakas2007multi}
from an ordinary binary classifier object
by constructing one binary classifier per class
(a strategy variously called one-vs.-the-rest,
one-vs.-all or binary relevance).
